pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-07 manuscript/greenwell.tex
minor edits

For a more customizable plot, call \code{partial} with \code{plot = FALSE} and use the \code{plotPartial} function. \strong{Note:} the \dfn{pipe} operator \code{\%>\%} provided by the \CRANpkg{magrittr} package \citep{magrittr-pkg} is exported for writing more convenient code, as illustrated in snippet of code below which increases the line width, adds a LOESS smoother, and customizes the $y$-axis label.
\begin{example}
boston.rf %>%
  partial(pred.var = "lstat") %>%
  plotPartial(smooth = TRUE, lwd = 2, ylab = expression(f(lstat)))
\end{example}
The result is displayed in the right side of Figure~\ref{fig:pd_lstat} below.

>>>>

For a more customizable plot, call \code{partial} with \code{plot = FALSE} and use the \code{plotPartial} function. \strong{Note:} the \dfn{pipe} operator \code{\%>\%} provided by the \CRANpkg{magrittr} package \citep{magrittr-pkg} is exported for writing more convenient code, as illustrated in the example below which increases the line width, adds a LOESS smoother, and customizes the $y$-axis label.
\begin{example}
boston.rf %>%
  partial(pred.var = "lstat") %>%
  plotPartial(smooth = TRUE, lwd = 2, ylab = expression(f(lstat)))
\end{example}
The result is displayed in the right side of Figure~\ref{fig:pd_lstat} below.
